% -- Encoding UTF-8 without BOM
% -- XeLaTeX => PDF (BIBER)

\documentclass[]{cv-style}          % Add 'print' as an option into the square bracket to remove colours from this template for printing.
                                    % Add 'espanol' as an option into the square bracket to change the date format of the Last Updated Text

\sethyphenation[variant=british]{english}{} % Add words between the {} to avoid them to be cut

\begin{document}

\header{Carlos Alexander}{~Vializ}           % Your name
\lastupdated

%---------------------------------------------------------
%	SIDEBAR SECTION
%    -- In the aside, each new line forces a line break
%---------------------------------------------------------

\begin{aside}
%
\section{contact}
72 West 82nd Street
Apt 2R
New York, NY 10024
~
\texttt{\color{gray}(650) 422-9057}
\texttt{\color{gray}(209) 800-CLOS}
\texttt{\color{gray}          2567}
~
\href{mailto:carlos@vializ.me}{carlos@vializ.me}
\href{https://www.vializ.me}{www.vializ.me}
\href{https://www.github.com/cvializ}{github.com/cvializ}
\href{https://www.twitter.com/closvvvvvv}{@closvvvvvv}
%
\section{programming}
Windows \& Unix shell, JS\,(Node\,\&\,DOM), C, Java, C\#, Python, SQL, Assembly, Morse, Smoke signals, \LaTeX{}%
\\[\baselineskip]%
WAI-ARIA, WCAG, HTML5, CSS3, ECMAScript 2019, REST, WebSockets %
\\[\baselineskip]%
{Vanilla~JS}, React, Angular, Chai, Mocha, Istanbul, Karma, Gulp, Bundling tools%
%
\section{interests}
\textbf{professional:} Responsive and accessible web design, real-time app development, clean straightforward code. Volunteer tutoring English literacy and computer skills.\\[\baselineskip]%
\textbf{personal:} Aviation/Aerobatics ({Piper~Cherokee},\\{C172}, C182, Citabria, {Super~Decathlon}), Hiking, Camping, Climbing, Biking, Unicycling, Photography, Español
%
\end{aside}

%---------------------------------------------------------
%	WORK EXPERIENCE SECTION
%---------------------------------------------------------

\section{experience}

\begin{entrylist}

%------------------------------------------------
\entry
  {2016--now}
  {Google}
  {New York, NY}
  {\jobtitle{Software Engineer, Open Source AMP Project}
  \begin{itemize}
    \item Subject matter expert for web form and user input related components, like amp-form, amp-date-picker and amp-inputmask.
    \item Implemented abstract end-to-end testing framework: a common API for multiple Web Driver implementations to improve standards and flakiness.
    \item Tech Lead for amp-autocomplete project, overseeing a junior developer and coordinating between PM, design and stakeholders.
  \end{itemize}}
%------------------------------------------------
\entry
  {2015--2016}
  {Kifi}
  {Mountain View, CA}
  {\jobtitle{Lead UI/UX Engineer}
  \begin{itemize}
    \item Developed and designed \textit{Kifi for Teams} UI to add an additional layer of information to the architecture of the consumer facing product.
    \item Maintained extension and code injection framework that must work on all webpages, including dynamically injecting search results into Google. Kifi results displayed faster than Google's. Extension rated\score{4.5}{5} by users.
    \item Released Safari extension by building abstraction around Safari Extension API.
    \item Improved contacts search list with real-time typeahead, with client-side caching for responsive performance.
    \item Acquired by Google
  \end{itemize}}
%------------------------------------------------
\entry
  {2014--15}
  {Visa, Inc.}
  {Foster City, CA}
  {\jobtitle{UI/UX Engineer, Visa Checkout}
  \begin{itemize}
    \item Architected CSS framework for reusable common components, utilizing flexible Node tools e.g. PostCSS.
    \item Increased conversion of shopping sales by over 15\%, driving millions in transactions.
  \end{itemize}}
%------------------------------------------------
\entry
  {2013}
  {Tridium, Inc.}
  {Richmond, VA}
  {\jobtitle{Software Engineer Intern}
  \begin{itemize}
    \item Developed a reusable HTML5 chart system for the Niagara/BajaScript equipment automation platform.
    \item Implemented Java annotation processors to reduce boilerplate in Niagara API.
  \end{itemize}}
\end{entrylist}

%---------------------------------------------------------
%	EDUCATION SECTION
%---------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2010--14}
{B.S. Computer Science. Mathematics Minor. {\normalfont Virginia Tech}}
{Blacksburg, VA}
{Focus: Algorithms and systems programming. Language, parser, and compiler design and implementation. Debugging, from IDE to gdb. Electives: Parallel computing with OpenMP, Pthreads, MapReduce; Human-Computer Interaction; Creative Computing Capstone: intersecting art and technology.}
%------------------------------------------------
\end{entrylist}

%---------------------------------------------------------
%	AWARDS SECTION
%---------------------------------------------------------

\section{qualifications and awards}
\begin{entrylist}
%------------------------------------------------
\entry
{2013}
{Private Pilot Certificate}
{Federal Aviation Administration}
{\vspace{-1.0cm}}
%------------------------------------------------
\entry
{2013, 2014}
{Scholarship for Academic Merit}
{Zora and Gilmer Warfield Scholarship Fund}
{\vspace{-1.0cm}}
%------------------------------------------------
% \entry
% {2014}
% {Scholarship for Academic Merit}
% {Virginia Tech Computer Science Research Consortium}
% {\vspace{-1.0cm}}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------

\section{projects}
\begin{entrylist}
%------------------------------------------------
\entry
{2014}
{The Resistance Universe: Coup}
{http://coup.vializ.me}
{A realtime, multi-room, online version of Coup, the popular dystopian tabletop game.}
%------------------------------------------------
\entry
{2014}
{Aviation Weight and Balance}
{http://wab.vializ.me}
{An extensible, interactive weight and balance calculator to determine aircraft loading.}
%------------------------------------------------

%----------------------------------------------------------------------------------------

\end{entrylist}
\end{document}
